Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-13 sections/correlated-sicm-and-fm.tex
commented the nanoinjection section. Is it really necessary?

Seifert et al. \cite{Seifert2017} investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton.
In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
myocyte-myofibroblast connection was linked to the expression of connexin-43
\cite{Schultz2019}.

@@

%% Wenn ich das Paper richtig verstehe, wurde hier aber kein konfokales FM
%% genutzt, oder? 
%
% Nashimoto et al. investigated whether the secretion of the von 
% Willebrand factor from living cells can be investigated by SICM without any
% additional labeling. , it is not always necessary to label the protein. Even with SICM alone the 
% detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
% images \cite{Nashimoto2015}.

% \subsection{\emph{Indirect} combination of SICM and FM}

% Beside \emph{direct} combinations in one instrument and correlations, which are displaying 
% images obtained by SICM and fluorescence microscopy of the same cell/same region, also 
% \emph{indirect} correlations exist. They are showing images under comparable conditions and 
% extent the investigation to aspects, which could not be obtained by using one technique alone. 
% Such \emph{indirect} correlations were used for investigating the uptake of nanotubes 
% \cite{Lee2013}, nanoparticles \cite{Gesper2017} or for investigating healthy and failing 
% myocytes \cite{Lyon2009}. Nevertheless is it important to mention, that they could just giving 
% hints of correlations, it is not directly comparable with investigations of both in the same 
% cell.

@@

\subsection{Nanoinjection of fluorescently labeled molecules}

Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
could be also used for nanoinjection of fluorescently labeled molecules into living cells 
\cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
introduced into the membranes, could occur \cite{Hennig2015a}.

The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
the diffusion of single molecules over different regions at a spermatozoa were investigated.

The SICM-nanopipette could be also used for investigating membrane rafts 
\cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.

Another example for a SICM-nanopipette based manipulation could be found in the study on the 
generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
be used for the detection of Calcium \cite{Wang2020}.

% Piper2006 -> PMID: 17177370
The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
\cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
of the pH value or the concentration of ions with alterations in the detected fluorescence signal.

>>>>

Seifert et al. \cite{Seifert2017} investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton.
In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
myocyte-myofibroblast connections was linked to the expression of connexin-43
\cite{Schultz2019}.

@@

@@

% \subsection{Nanoinjection of fluorescently labeled molecules}

% Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
% the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
% fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
% could be also used for nanoinjection of fluorescently labeled molecules into living cells 
% \cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
% optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
% stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
% introduced into the membranes, could occur \cite{Hennig2015a}.

% The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
% combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
% In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
% the diffusion of single molecules over different regions at a spermatozoa were investigated.

% The SICM-nanopipette could be also used for investigating membrane rafts 
% \cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
% functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
% focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
% was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.

% Another example for a SICM-nanopipette based manipulation could be found in the study on the 
% generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
% cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
% generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
% be used for the detection of Calcium \cite{Wang2020}.

% % Piper2006 -> PMID: 17177370
% The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
% \cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
% of the pH value or the concentration of ions with alterations in the detected fluorescence signal.
